|

### 2019-05-16 appendix/freire-mignozzetti-skarbek-appendix.Rmd
add appendix files

---
title: "Supplementary Materials for: Do Elites Support Polycentric Climate Governance? Evidence from Ten Latin American Countries"
author: 
- "Danilo Freire[^freire]"
- "Umberto Mignozzetti[^mignozzetti]"
- "David Skarbek[^skarbek]"
date: "15 May 2019"
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: no
    template: template.latex
header-includes:
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
---

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plm); library(tidyverse)
library(haven); library(clusterSEs)
library(stargazer); library(cjoint)
library(sp); library(cregg)
library(kableExtra)
setwd("~/Documents/github/polycentrism/appendix/")
load('freire-mignozzetti-skarbek.RData')

@@

```{r}
## Main model
rm(cj)
setwd("~/Documents/github/polycentrism/appendix/")
load('freire-mignozzetti-skarbek.RData')
# Set conjoint baselines
baselines <- list()
baselines$`How often will the agreement be renegotiated?` <- "One year"
baselines$`What punishments do they use?` <- 'None'
baselines$`How are conflicts resolved?` <- 'Government bureaucracy'
baselines$`How are costs distributed?` <- 'Rich countries pay more than poor countries'
attrs <- 
  c("How are conflicts resolved?",
    "How are costs distributed?",
    "How are repeated violations punished?",
    "How often will the agreement be renegotiated?",
    "What punishments do they use?",
    "Who makes the rules?"
    )

>>>>

---
title: |
       | Supplementary Materials for "Do Elites Support Polycentric Climate Governance? Evidence from Latin American Countries"
author: 
- "Danilo Freire[^freire]"
- "Umberto Mignozzetti[^mignozzetti]"
- "David Skarbek[^skarbek]"
date: "16 May 2019"
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: no
    template: template.latex
header-includes:
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
---

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plm); library(tidyverse)
library(haven); library(clusterSEs)
library(stargazer); library(cjoint)
library(sp); library(cregg)
library(kableExtra)
load('freire-mignozzetti-skarbek.RData')

@@

```{r}
## Main model
rm(cj)
load('freire-mignozzetti-skarbek.RData')
# Set conjoint baselines
baselines <- list()
baselines$`How often will the agreement be renegotiated?` <- "One year"
baselines$`What punishments do they use?` <- 'None'
baselines$`How are conflicts resolved?` <- 'Government bureaucracy'
baselines$`How are costs distributed?` <- 'Rich countries pay more than poor countries'
attrs <- 
  c("How are conflicts resolved?",
    "How are costs distributed?",
    "How are repeated violations punished?",
    "How often will the agreement be renegotiated?",
    "What punishments do they use?",
    "Who makes the rules?"
    )
